### 2016-03-10 paper/introduction.tex
yasu

\section{Introduction}
Parallel computation has changed the field of computing.  In the 90s,
most processors had single cores. In 2016, most processors have multiple
cores, often 4 or even 8. Cluster computing further expands the
potential of parallel computation, where one can easily launch a
processing job using hundreds or even thousands of computational nodes
in a cloud.

Parallel computation offers tremendous potential for Computer Vision. As
image sensing technologies have gone through revolutions, we are in
ever growing demands in solving very large problems. One may need to
apply image denoising to 50 Megapixel images from latest digital
SLRs~\cite{canon?}, stitch thousands of images to generate gigapixel
panoramas~\cite{gigapan}, or solve volumetric reconstruction and
segmentation problems over a billion ($=1024^3$)
voxels~\cite{Joint3DSceneReconstructionandclassSegmentation}.
%
However, state-of-the-art algorithms are still inherently sequential in
many Computer Vision problems. Take a Fusion-Move algorithm
(FM)~\cite{viktor,second_order_stereo,else} for Markov Random Field
inference, for example. FM has been one of the most effective techniques
in solving the above
problems~\cite{fusion_moves_for_markov_random_field_optimization}.
%
It sequentially improves solution by fusing the current solution with a
solution proposal. FM allows domain-specific customization of proposal
generation schemes, a main advantage over general solvers such as
message passing algorithms~\cite{TRW,loopy_belief_propagation}.  Its
successful applications range from optical flow, stereo, image
denoising, image inpainting, to image
segmentation~\cite{fusion_moves_for_markov_random_field_optimization}.

@@

>>>>

\section{Introduction}
Parallel computation has changed the field of computing.  In the 90s,
most processors had single cores. In 2016, most processors have multiple
cores, often 4 or even 8. Cluster computing further expands the
potential of parallel computation, where one can easily launch a
processing job using hundreds or even thousands of computational nodes
in a cloud.
%
In the recent work on Go (AlphaGo from DeepMind), parallelization plays
a key role in the Monte-Carlo tree search~\cite{nature_alpha_go}.

Parallel computation offers tremendous potential for Computer Vision. As
image sensing technologies have gone through revolutions, we are in
ever growing demands in solving very large problems. One may need to
apply image denoising to 50 Megapixel images from latest digital
SLRs~\cite{canon?}, stitch thousands of images to generate gigapixel
panoramas~\cite{gigapan}, or solve volumetric reconstruction and
segmentation problems over a billion ($=1024^3$)
voxels~\cite{Joint3DSceneReconstructionandclassSegmentation}.
%
%
However, state-of-the-art algorithms are still inherently sequential in
many Computer Vision problems. Take a Fusion-Move algorithm
(FM)~\cite{viktor,second_order_stereo,else} for Markov Random Field
inference, for example. FM has been one of the most effective techniques
in solving the above
problems~\cite{fusion_moves_for_markov_random_field_optimization}.
%
It sequentially improves solution by fusing the current solution with a
solution proposal. Its successful applications range from optical flow,
stereo, image denoising, image inpainting, to image
segmentation~\cite{fusion_moves_for_markov_random_field_optimization}.

@@

%1. In the introduction, we could mention the recent work on Go (DeepMind's AlphaGo Nature paper) in which parallization plays a key role in the monte carlo search.

%2. Yasu, your explanation of the advantages of Fusion Move (described in
%section 2) is correct. In the sentence on "Second, FM can handle
%problems with very large label spaces.." we could add "and even
%real-valued variables".

3. I would suggest removing "Genetic algorithms" from the paragraph heading at the end of section 2 or replacing it with "Evolutionary Algorithm".

4. We should cite two more papers
(a) Hierarchical Graph cuts (Kumar and Koller, UAI 2009)
(b) Making the right move (Batra and Kohli, CVPR 2010)
